### 2013-12-02 proposal/proposal/chapter2.tex
changes

        The second criteria is called the \emph{feasibility} condition,
        according to which, the payoff for each agent cannot be more than
        the coalition total gain. A payoff vector is also \emph{efficient}
        if the payoff obtained by a coalition is distributed amongst the
        coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
        the characteristic function works in \emph{transferable utility}
        (TU) settings, where utility (i.e., payoff) is transferable from
        one player to another, or in other words, players have common
        currency and a unit of income that is worth the same for all players
        \cite{myerson1991game}.

@@

            \emph {THIS EXAMPLE IT NOT COMPLETE YET}

@@

            \begin{example}\label{ex:simplecorealpha}
                In this example, we want to analyse games under conditions which core can be empty. Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $(x_1,x_2,x_3)$ distribution vector is in $core$ if $x \geq 0$, $\forall i, \forall j, x_i + x_j \geq \alpha $
            \end{example}

            \begin{example}\label{ex:simplecore2}

                An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
                This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).

                In this game, land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output. The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$. The preference of each player would be the amount of out she obtains.

                In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
                is in the core: all coalitions that can produce any output include the landowner, and none of these
                coalitions has any actions that makes her better off than she is in $a_{N}$.

                For any value of n The core contains actions in which the workers receive some output.
                The workers need the landowner to produce any output, but the landowner
                also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
                workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
                coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
                on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
                coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
                Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
                Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
                $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
                $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
                That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
                is in the core, as you are asked to verify in the following exercise.

            \end{example}

@@

        % THIS IS REPEATED
        \emph {-- this is repeated --}
        In this research work, we use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.

>>>>

        The second criteria is called the \emph{feasibility} condition,
        according to which, the payoff for each agent cannot be more than
        the coalition total gain. A payoff vector is also \emph{efficient}
        if the payoff obtained by a coalition is distributed amongst the
        coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
        the characteristic function works in \emph{transferable utility}
        (TU) settings, where utility (i.e., payoff) is transferable from
        one player to another, or in other words, players have common
        currency and a unit of income that is worth the same for all players
        \cite{myerson1991game}.

@@

@@

            \begin{example}\label{ex:simplecorealpha}
                In this example, we want to analyse games under conditions which core can be empty. Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $(x_1,x_2,x_3)$ distribution vector according to equation \ref{eq:core}, is in $core$ if $x_i \geq 0$ which implies each player will get more than 0 which they would when working alone and $\forall i, \forall j, x_i + x_j \geq \alpha $ which implied any pair of players will get more than $\alpha$ which they would earn if they worked in pair without the third player and finally $\sum_{i \in N} x_i = 1$ which implied all the gain is distributed among the three players. Based on these three equations we have, $\forall i \in N 0 \leqslant 1 - \alpha$ and $\sum_{i \in N} x_i = 1$. By summing first equation for all three platers, we conclude $Core (N,v)$ is nonempty iff $\alpha \leqslant \frac{2}{3}$. When alpha is more than $\frac{2}{3}$, the contribution of third player is not good enough to justify the group of three players working together. The third player will increase the revenue with less then $\frac{1}{3}$, and the other two players, both can get better share of revenue if they work together. This is why the group of three players working together when $\alpha > \frac{2}{3}$ is not stable.
            \end{example}

            %\begin{example}\label{ex:simplecore2}
%
%                An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
%                This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).
%
%                In this game, land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output. The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$. The preference of each player would be the amount of out she obtains.
%
%                In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
%                is in the core: all coalitions that can produce any output include the landowner, and none of these
%                coalitions has any actions that makes her better off than she is in $a_{N}$.
%
%                For any value of n The core contains actions in which the workers receive some output.
%                The workers need the landowner to produce any output, but the landowner
%                also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
%                workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
%                coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
%                on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
%                coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
%                Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
%                Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
%                $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
%                $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
%                That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
%                is in the core, as you are asked to verify in the following exercise.
%
%            \end{example}

@@

        In this research work, I will use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.
